A neural coarse graining theory of consciousness/\newline Non-trivial Informational closure through neural coarse-graining as the Fundamental Informational Correlates of Consciousness

### 2019-04-17 Paper_neural_coarse_graining_of_consciousness.tex

% =================================== Macro ================================== %
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[at]{easylist}
\usepackage{tcolorbox}
\tcbuselibrary{skins}
\usepackage{comment}
\usepackage[framemethod=tikz]{mdframed}
\usetikzlibrary{shadows}
\usepackage{soul}

@@

	% Writing Materials
    \newenvironment{writingMaterials} %
    	{
            \begin{tcolorbox}[enhanced,
                title=-,
                size=small,
                colbacktitle=Aquamarine,
                drop fuzzy shadow,
                fontupper=\small,
                boxrule=0.4pt,
                colback=Aquamarine!10!white,
                sharp corners]
                Writing Materials
            \end{tcolorbox}
            \begin{easylist}[itemize]
    	}
    	{
            \end{easylist}  
            \begin{tcolorbox}[enhanced,
                halign=flush right,
                halign title=right,
                size=small,
                colbacktitle=Aquamarine,
                drop fuzzy shadow,
                fontupper=\small,
                boxrule=0.4pt,
                colback=Aquamarine,
                colupper=White,
                sharp corners]
                Writing Materials -
            \end{tcolorbox}        
    	}

@@

		% figure todo
		\newcommand{\includegraphicsTodo}[2][]{%
			\tcbox[%
				adjusted title=\LARGE To Be Modified,
				halign title=right,
				colbacktitle=Orange!75!White,
				coltitle=Black,
				colframe=Red!60!White,
				boxrule=1mm,
				colback=white%
				]{\includegraphics[#1]{#2}}}

@@

	% communication: green
		% call for help
			\newcommand{\callforhelp}[1]{\todo[color=SpringGreen]{[Call For Help]: #1}}

@@

@@

		\begin{writingMaterials}
			@ Consciousness as an intrinsic information. Therefore, information should be self-define. This means the boundary of conscious content should be related to informational closure.

@@

		\end{writingMaterials}

@@

		\begin{writingMaterials}
			@ \rewrite{
				Coarse-graining: a method of reducing the complexity of a system by treating groups of atoms/molecules as single quasi-particles CG: coarse-grained}

@@

			%% Macroscale Deterministic
			@ The environment that human scale agents interact with is approximately govern by Newton's law and therefore the state transitions are nearly deterministic.\callforhelp{Is there any good ref I can cite?}

@@

		\end{writingMaterials}

		\begin{comment}

@@

			\begin{writingMaterials}
				@ Population coding

@@

			\end{writingMaterials}

			\begin{comment}
				@ Achieving NTIC is the key objective to to extract out latent control parameters in the environment.

@@

				@ Agents can process information and act at abstract levels
			\end{comment}

			\begin{comment}
				@ At the physical scale which human being live, the environmental dynamics is nearly deterministic following the laws of classical physics. This means that it is possible for agents living at this physical scale to build NTIC process internally.

				@ When the information in individual sensory channel is noisy and partial, coarse-graining becomes necessary for achieve NTIC.
			\end{comment}

@@

\rlstart{4}
        In this section, we propose a new theoretical framework of consciousness \{\tnamefull\} \todo{We need a good name}. This framework proposes that NTIC is the fundamental properties for information processing to be conscious. Additionally, coarse-graining is necessary to achieve NTIC in various of different systems.

        We starts our argument from a presumptive fact that every human conscious precept is highly informative. Our conscious experience always consists of high multidimensional information and usually involves information from multiple modalities. If we consider information as resolved uncertainty, every conscious percept rules out other enormous possible conscious states that we are able to experience. Therefore, every conscious percept resolves a huge amount of uncertainty and provides considerable information.

@@

        Based on this presumptive fact, we postulate that the amount of information possessed of a conscious percept should be equivalent to information that we can obtain from a particular physical event in the physical reality. For example, considering two physical systems (Alice and Bob) and there is no interaction (or information passing) in between. Assuming that Alice is conscious, the conscious experience that Alice has should not involve any information about Bob.

@@

        We further take a radical standpoint and postulate that consciousness fundamentally associates with information in the physical reality, i.e. information correlates of consciousness (ICC), \cite{chalmers1996conscious, tononi2004information, gamez2011information}) and discard the notion of neural correlates of consciousness(NCC). In sum, we consider consciousness is an information-based phenomenon and information is a common language between conscious experience and the physical world.

        We next consider the boundary problems of consciousness \cite{goff2006experiences}. Even though information involved in every conscious percept is extremely rich, it is still bounded, i.e. the boundaries of information exist in every conscious percept. Presuming consciousness is information-based, we can identify the boundaries by measures from information theory. Particularly in this case, boundaries can be defined by information closure. More importantly, our conscious experience always contains not merely trivial informational. Rather, it always provides rich information about the environmental and our bodily states. Therefore, we postulate that NTIC is a fundamental informational property associated with consciousness.

        Through coarse-graining, to achieve NTIC processes becomes possible in the neural system at macroscopic levels. Therefore, coarse-graining becomes necessary because every individual sensor and neuron at the microscopic scale can only access and process very limited partial information (Fig. \ref{fig:LevelOfConsciousness}). In the following, ...

		\begin{writingMaterials}

@@

		\end{writingMaterials}

		\begin{writingMaterials}

@@

		\begin{writingMaterials}
            @ Our theory naturally explains the compositional nature of consciousness because the joint states of entities in the NTIC process determine the contents of consciousness.

		\end{writingMaterials}

@@

			\begin{writingMaterials}
    			@ This implies that, based on the Equation \ref{eq:nticObjective}, the self-predictive information about the future states that the current state holds and the information about the environment encoded in the process determine the level of consciousness.

@@

@@

            \begin{writingMaterials}
    			@ Of course, from evolutionary perspective, neural system should develop a better hardware to support neural coarse-graining

@@

				@ It is possible that the neural system represents higher-level information processing by low level physical subtract. For example, studies have found representation for summery statistics of signal and neural. population.\needref{neural representation for summery statistics}\\
				From this point of view, sensory hierarchy may extend along with levels of coarse-graining.
            \end{writingMaterials}
\rlend

@@

\rlstart{2}	
		\ideaBox{The goal of this part is to combine empirical study and phenomenology}
		Our theory suggests two necessary conditions to make information conscious in the neural system.
		\begin{enumerate}
		    \item The information needs to be encode in NTIC processes
		    \item \highlightAndComment{The information exists at coarse-grained levels which creates a high degree of NTIC and reduces stochasticity}{Need better expressions} 
		\end{enumerate}

@@

		\subsection{Conscious Processing}
		    \begin{ants}
		        @ To achieve high NTIC has evolutionary advantage.

		        @ The current state of the process contains the information about its future state. Therefore, the neural system can build forward models to predict the future state of the environment using the information encoded in the NTIC process.

		        @ Cognitive functions recruiting forward models built upon it are conscious. (E.g., planning, imagination, dreaming)

		        @ It is important to note that we do suggest any functionalism of consciousness. Rather, we believe that information is fundamentally linked to consciousness. The reason why consciousness is accompanied with some specific cognitive function is because NTIC is a powerful property that brings creatures a lot of advantage in the evolution.

@@

		\subsection{Unconscious Processing}
		    \begin{ants}
    		    @ When processes fail to satisfy either of the two conditions, they remain unconscious.

    		    @ When processes do not meet the first condition, i.e. the information processed not at the certain coarse-grained level, the information will not be included in conscious contents.

    		    @ For example, we are never conscious of neural spike activities at microscopic levels (e.g. single cell activities) because information passing among individual neurons are not at the certain coarse-grained level.

    		    @ Libet's free will experiment can be also explained by our theory.

    		    @ The random neural fluctuation under Libet's free will experiment happens at the microscopic scale \citep{SchurgerE2904}.

    		    @ When processes do not meet the second condition, i.e. processes which do not achieve high NTIC will remain unconscious.

    		    @ This can explain why many "policy-based" processes are not conscious.

    		    @ Policy-based here features those processes taking sensory information as input and directly outputting actions. Therefore, the future states of policy-based processes largely depend on the environmental states and failed to achieve informational closure.

    		    @ Several neural processes are included in this category, e.g. reflexive neural circuit, blindsight, procedure memory. 
		    \end{ants}

        \subsection*{}
            \begin{ants}
                @ To summarise, our theory can well explain the various findings with parsimonious assumptions. 
            \end{ants}

@@

	\section{Comparison with other theories}
		\ideaBox{Main points should be same/diff, our advantages, and predictions}
		\begin{ants}
		    @ In this section, we will discuss the relationship between our theory and other popular modern theories of consciousness. 
		\end{ants}

\rlstart{1}
		\subsection{Theories about multilevel views on consciousness and cognition}
			\begin{ants}
			    @ Previously, multilevel views on consciousness and cognition have been proposed.

			    @ In the following, we discussed the differences between our theory and other theories about multilevel views.

			\begin{writingMaterials}
			    @ LEVELS OF ORGANIZATION \cite{wimsatt1994ontology}

			    @ As mentioned previously, the level of coarse-graining is different from the anatomical level.

			    @ \ideaBox{Should I also deal with Marr's level of abstraction?}

			    @ See the discussion in \cite{pennartz2015brain}. But Pennartz focus more on multimodal representation as the most important factor.

			    @ Our proposal is inline with Pennartz's Neurorepresentational theory (Neurorepresentationalism). \cite{pennartz2018consciousness,pennartz2015brain}.

			    @ Some theories also address the relationship between level of processing and consciousness.

			    @ However, it’s crucial to note that our theory claims only the level of coarsegraining achieving NTIC matters to connsciousness rather than the anatomical level of sensory hierarchy

				@ We shortly describe two theories which is \todo{XXX and XXX} related to our current proposal.			    
			\end{writingMaterials}

			\subsubsection{Intermediate Level Theory} \label{IntermediateLevelTheory}
				\begin{ants}
				@ Intermediate Level Theory (ILT) proposes that conscious experience only correlates specific levels of representations in the sensory processing the hierarchy. This theory claims that consciousness only associates with the representation at  intermediate levels rather than the ones at lower-level or higher-level.

				@ As mentioned previously, a critical difference between ILT and our theory is that our theory doesn't assume the direction of coarse-graining should align with the direction of anatomical processing levels along cortical hierarchies (see fig \ref{fig:hierarchy}).
				\end{ants}

			\subsubsection{Pennartz's neurorepresentational theory (Neurorepresentationalism)}
			    \begin{ants}
			    @ Our theory shares some similar concepts with Pennartz's Neurorepresentationalism.

		        @ However, Neurorepresentationalism focuses on multimodal representation.

		        @ Neurorepresentationalism also focuses on "making sense" between representation

		        @ We focus on informational closure which suggests the closure of causal interaction in a system.

		        @ We don't assume any functional properties as the criteria of consciousness. Instead, we propose information as a more fundamental principle correlates consciousness.  
			    \end{ants}

				\begin{writingMaterials}
					%% Back up materials

@@

				    @ Our prediction is, if information that is carried by v1 neurons are necessary to complete informational closure, the states of V1 neurons should also co-vary with conscious contents.

@@

					%% Our theory
					@ However, as we mentioned in Section \ref{sec:SensoryHierarchy}, \rewrite{The notion of ‘ levels ’ deployed here is functional and very different from that of successive anatomical processing stages along cortical hierarchies [75] or from anatomic scales in the brain. The multi-level concept in [2] is more akin to Marr ’ s original distinction between the levels of (neural) implementation, algorithms, and computational theory [122], but focuses on how conscious representations correspond to computational operations at levels with lower complexity and representational capacity.}\cite{pennartz2018consciousness,pennartz2015brain}
				\end{writingMaterials}

@@

\rlstart{1}	
		\subsection{First-order theories}

		    @ The ﬁrst-order theories suggest that consciousness is determined by early sensory information or neural activities.\needref{First-order theories}

		    @ We suggest that, if early sensory information or neural activities after coarse-graining take parts in the NTIC process, early sensory information or neural activities also contribute consciousness.

		    @ However, due to coarse-graining, changes of early sensory information or neural activities do not necessarily accompany with changes of conscious contents.

			\begin{writingMaterials}
				@ \rewrite{
					The ﬁrst-order view maintains that conscious awareness is determined by early sensory activity alone, independently of higher-order representations. Thus the crucial difference between the ﬁrst-order and higher-order views is that the latter but not the former predict that conscious awareness is determined at least in part by prefrontal and parietal activity. Therefore, in the group of ﬁrst-order theorists we include here not only those commonly labeled as such in the philosophical literature [11] but also theorists, such as Ned Block [12,13], who hold that the phenomenal qualities of awareness depend on the biological substrate rather than merely the content of the ﬁrst-order representations, as well as scientists who hold that visual awareness depends on activity in content-speciﬁc regions of the extrastriate cortex [24,25] or on feedback from these regions to the primary visual cortex [26]. Most ﬁrst-order theories explain the difference between awareness and unawareness by positing that the latter is associated with weak information [29] or with representations in alternative (e.g. subcortical) sensory pathways. Thus this view suggests that conscious and unconscious processing will have different functional consequences. Whereas some ﬁrst-order theorists hold that some higher cognitive functions can be performed without conscious awareness [30–32], most ﬁrst-order theorists take a difference in perceptual task performance (e.g. ‘hits’ vs ‘misses’ in a detection task) as evidence for a difference in conscious awareness [12,13,25,26,33]. In other words, they typically associate task performance with awareness..} \cite{lau2011empirical}

@@

\rlstart{1}
		\subsection{Higher Order Thought theory of consciousness}
			\idea{
				People think a high order representation receives information from the first order representation. This may be a misunderstanding. This may be the result of neural coarse-graining. Because contents in informational closure look like watching fine-grained information, people may have an wrong impression about it}

			============================================================================
			\begin{ants}
			    @ In contrast to first-order theories, higher-order thought theories suggest that consciousness depends on higher-order representations representing agents as being in particular internal states.

@@

				@ \cite{rosenthal2005consciousness}
			\end{ants}

            \begin{writingMaterials}
			@ \rewrite{
				Higher-order theories of consciousness argue that conscious awareness crucially depends on higher-order mental representations that represent oneself as being in particular mental states.} \cite{lau2011empirical}

@@

\rlstart{1}
		\subsection{Global workspace theory}

				%% Introduction
				@ Global workspace theory (GWT)\cite{baars1988cognitive, baars1997theatre, baars2002conscious} or Global Neuronal Workspace theory (GNWT)\cite{dehaene1998neuronal, dehaene2001towards, dehaene2011experimental} states that the neural system consists of many separate specialised modules and a central global workspace (GW) which integrates and passes information amount the modules. Only the information that is accessed by the global workspace can be conscious aware of. The modules competes with each other to gain the access to the global workspace and the information from the winner can trigger an all-or-none "ignition" in the global workspace and be globally broadcasted to other modules. Conscious contents then associates information which gains access to the internal global workspace \cite{Dehaene2017}.

>>>>

% =================================== Macro ================================== %
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[at]{easylist}
\usepackage{tcolorbox}
\tcbuselibrary{skins}
\usepackage{comment}
\usepackage[framemethod=tikz]{mdframed}
\usetikzlibrary{shadows}
\usepackage{soul}
\usepackage{version}

@@

	% Writing Materials
    \newenvironment{WritingMaterials} %
    	{
            \begin{tcolorbox}[enhanced,
                title=-,
                size=small,
                colbacktitle=Aquamarine,
                drop fuzzy shadow,
                fontupper=\small,
                boxrule=0.4pt,
                colback=Aquamarine!10!white,
                sharp corners]
                Writing Materials
            \end{tcolorbox}
            \begin{easylist}[itemize]
    	}
    	{
            \end{easylist}  
            \begin{tcolorbox}[enhanced,
                halign=flush right,
                halign title=right,
                size=small,
                colbacktitle=Aquamarine,
                drop fuzzy shadow,
                fontupper=\small,
                boxrule=0.4pt,
                colback=Aquamarine,
                colupper=White,
                sharp corners]
                Writing Materials -
            \end{tcolorbox}        
    	}

    % \excludeversion{WritingMaterials}

@@

	% figure todo
        \newcommand{\includegraphicsTodo}[2][]{%
            \tcbox[enhanced,
                center,
            	adjusted title=\large To Be Modified ...,
            	halign title=center,
            	attach boxed title to top left={yshift=-3mm, xshift=1cm,yshifttext=-1mm}, boxed title style={drop fuzzy shadow},
            	colbacktitle=RedOrange!70!black,
            	coltitle=white,
            	colframe=RedOrange!50!black,
            	colback=white
        	]{\includegraphics[#1]{#2}}}

@@

	% communication: green
		% call for help
			\newcommand{\needhelp}[1]{\todo[color=SpringGreen]{[Need Help]: #1}}

@@

    % backup: 
    \newenvironment{backup}
    {

        \begin{tcolorbox}[enhanced,
            title=-,
            size=small,
            colbacktitle=black!70!white,
            colback=black!10!white,            
            drop fuzzy shadow,
            fontupper=\small,
            boxrule=0.4pt,
            sharp corners]
            Backup
        \end{tcolorbox}
    }
    {
        \begin{tcolorbox}[enhanced,
            halign=flush right,
            halign title=right,
            size=small,
            colbacktitle=black!10!white,
            colback=black!70!white,
            drop fuzzy shadow,
            fontupper=\small,
            boxrule=0.4pt,
            colupper=White,
            sharp corners]
            Backup -
        \end{tcolorbox}    
    }
    % \excludeversion{backup}

@@

		\begin{WritingMaterials}
			@ Consciousness as an intrinsic information. Therefore, information should be self-define. This means the boundary of conscious content should be related to informational closure.

@@

		\end{WritingMaterials}

@@

		\begin{WritingMaterials}
			@ \rewrite{
				Coarse-graining: a method of reducing the complexity of a system by treating groups of atoms/molecules as single quasi-particles CG: coarse-grained}

@@

			%% Macroscale Deterministic
			@ The environment that human scale agents interact with is approximately govern by Newton's law and therefore the state transitions are nearly deterministic.\needhelp{Is there any good ref I can cite?}

@@

		\end{WritingMaterials}

		\begin{WritingMaterials}

@@

		\end{WritingMaterials}

			\begin{WritingMaterials}
				@ Population coding

@@

			\end{WritingMaterials}

			\begin{WritingMaterials}
				@ Achieving NTIC is the key objective to to extract out latent control parameters in the environment.

@@

				@ Agents can process information and act at abstract levels
			\end{WritingMaterials}

			\begin{WritingMaterials}
				@ At the physical scale which human being live, the environmental dynamics is nearly deterministic following the laws of classical physics. This means that it is possible for agents living at this physical scale to build NTIC process internally.

				@ When the information in individual sensory channel is noisy and partial, coarse-graining becomes necessary for achieve NTIC.
			\end{WritingMaterials}

@@

\rlstart{5}

        In this section, we propose a new theoretical framework of consciousness \{\tnamefull\} \todo{We need a good name}. This framework proposes that NTIC is the fundamental properties for information processing to be conscious. Additionally, coarse-graining is necessary to achieve NTIC in various of different systems.

        We starts our argument from the first presumptive fact that every human conscious precept is highly informative. Our conscious experience always consists of high multidimensional information and usually involves information from multiple modalities. The notion of information referred to in this article is considered as resolved uncertainty. Being a certain conscious state rules out other enormous possible conscious experience in the state space of conscious experience. Therefore, every conscious percept resolves a huge amount of uncertainty and provides considerable information.

@@

        Based on this presumptive fact, we postulate that the amount of information possessed of a conscious percept should be equivalent to information involved in a particular event or entity in the physical reality. Strictly speaking, we recognise information is a common language between conscious experience and the physical reality. We further take a radical standpoint and postulate that consciousness is fundamentally associated with information, i.e. information correlates of consciousness (ICC), \cite{chalmers1996conscious, tononi2004information, gamez2011information, Gamez2016}) and discard the notion of neural correlates of consciousness(NCC).

        Next, we next consider the second presumptive fact that the information in consciousness is bound. Even though information involved in every conscious percept is extremely rich, it is still limited and we do not consciously feel everything in this universe. This leads to the boundary problems of consciousness \cite{goff2006experiences}. There should exist information boundaries for every conscious entity. Presuming consciousness is information-based phenomenon, we can identify the boundaries with measures from information theory. Particularly, in this case, boundaries can be defined by information closure. Therefore, information closure should be observed in conscious entities in the physical reality.

        \rewording{informational closure also suggests that there is no information flow from the lower to the higher level. Knowledge of the microscopic levels will not improve predictions of the future states of the macroscopic levels \citep{PFANTE.2014}}. This indicates that informational closed macroscopic levels can be treated as a complete reality.

        Finally, our conscious experience always reflects some degree of information about environment and bodily states, i.e. non-trivial information. To account for the information-based considerations, we propose that NTIC is a fundamental informational property associated with consciousness.

        \begin{WritingMaterials}
        For example, considering two physical systems (Alice and Bob) and there is no interaction (or information passing) in between. Assuming that Alice is conscious, the conscious experience that Alice has should not involve any information about Bob.

@@

        However, in many systems, it is difficult to achieve NTIC at microscopic levels due to stochasticity. Through coarse-graining, NTIC processes become possible at macroscopic levels. Therefore, coarse-graining is necessary for many biological systems to implement NTIC processes, especially for the neural system (Fig. \ref{fig:LevelOfConsciousness}). In the following, we explained this framework and provide mathematical definitions and implications of ICC.  
        \end{WritingMaterials}

		\begin{WritingMaterials}

@@

@@

		\begin{figure}[H]
			\includegraphicsTodo[width=0.8\textwidth]{WritingMaterials/LimitCycle/PhaseCycle.pdf}
			\label{fig:limitCycle}
			\caption{Example of coarse-graining by a limit cycle process}
		\end{figure}

		\begin{equation}\label{eq:LimitCycleExample}
            \begin{array}{l}{\dot{y_1}=y_1-y_2-y_1\left(y_1^{2}+y_2^{2} \right)+\epsilon_{y_1}} \\ {\dot{y_2}=y_1+y_2-y_2\left(y_1^{2}+y_2^{2}\right)+\epsilon_{y_2}}\end{array}
		\end{equation}

		The noise sources, $\epsilon_{y_1}$ and $\epsilon_{y_2}$, are i.i.d with a normal distribution with mean $\mu=0$ a and varance $\sigma^{2}=1$

		\begin{WritingMaterials}
            @ Our theory naturally explains the compositional nature of consciousness because the joint states of entities in the NTIC process determine the contents of consciousness.

		\end{WritingMaterials}

@@

			\begin{WritingMaterials}
    			@ This implies that, based on the Equation \ref{eq:nticObjective}, the self-predictive information about the future states that the current state holds and the information about the environment encoded in the process determine the level of consciousness.

@@

				@ Consciousness and complexity \cite{Tononi1998}

@@

            \begin{WritingMaterials}
    			@ Of course, from evolutionary perspective, neural system should develop a better hardware to support neural coarse-graining

@@

				@ It is possible that the neural system represents higher-level information processing by low level physical subtract. For example, studies have found representation for summery statistics of signal and neural. population.\needref{neural representation for summery statistics}\\
				From this point of view, sensory hierarchy may extend along with levels of coarse-graining.
            \end{WritingMaterials}

@@

\rlstart{3}	
		\ideaBox{The goal of this part is to combine empirical study and phenomenology}
	    \ideaBox{I need to expend this section much more and more references}
		Our theory suggests two necessary conditions to make information conscious in the neural system.
		\begin{enumerate}
		    \item The information needs to be encode in NTIC processes
		    \item \highlightAndComment{The information exists at coarse-grained levels which creates a high degree of NTIC and reduces stochasticity}{Need better expressions} 
		\end{enumerate}

@@

		\subsection{Conscious Processing}
		So far, previous consciousness research has identified a set of perceptual and cognitive functions which not exclusively but frequently associate with consciousness.

		\needhelp{I need some suggestions of conscious function here.}
		\begin{ants}
            @ response inhibition 
            @ goal
            @ planning            
            @ conflict resolution
            @ error detection         
            @ task-switching
            @ working memory
            @ cognitive control 
            @ overriding automatic responses
            @ self-monitoring 
            @ global availability 
            @ integration             
            @ stabilisation
            @ information for off-line processing
            @ flexible routing of information
            @ integrates behaviour across time            
            @ tasks for long duration
            @ flexibility and the strategic use of that information for complex operations and decision-making 
            @ flexible and adjust our behavior to different contexts and goals
            @ complex visuomotor abilities
            @ conscious thought, reflection, reasoning, and temporally extended sense of self. 
            @ multiple alternative possibilities
            @ simulate alternative realities 
            @ imagination
            @ dreaming 
            @ anticipation
            @ intending
            @ replaying
            @ interpreting
            @ reflecting
            @ reasoning
            @ problem solving 
            @ deciding            
		\end{ants}

		To achieve high NTIC has evolutionary advantage. When a process achieves NTIC, the current state of the process contains the information about its future state (Eq. (5)). Therefore, the neural system can build forward models to predict the future state of the environment using the information encoded in the NTIC process. Cognitive functions recruiting forward models built upon it are conscious. (E.g., planning and imagination)

		It is important to note that we do suggest any functionalism of consciousness. Rather, we believe that information is fundamentally linked to consciousness. The reason why consciousness is accompanied with some specific cognitive function is because NTIC is a powerful property that brings creatures a lot of advantage in the evolution \cite{Seth2009Encyclopediaofconsciousness}.

	    \begin{WritingMaterials}
	        @ importantly, evidence suggests that those functions in some conditions do not require the involvement of consciousness. This evidences an important fact that consciousness is not necessay to these functions.

@@

	        @ Replaying past events

	        @ \rewrite{However, recent evidence also points out interesting dissociations between conscious and unconscious information processing when it comes to the duration, flexibility and the strategic use of that information for complex operations and decision-making} \cite{van2012role}

	    \end{WritingMaterials}

		\subsection{Unconscious Processing}
		When processes fail to satisfy either of the two conditions, they remain unconscious. First, when processes do not meet the first condition, i.e. the information processed not at the certain coarse-grained level, the information will not be included in conscious contents. For example, we are never conscious of neural spike activities at microscopic levels (e.g. single cell activities) because information passing among individual neurons are not at the certain coarse-grained level. \todo{Rewording}Libet's free will experiment can be also explained by our theory. The random neural fluctuation under Libet's free will experiment happens at the microscopic scale \citep{SchurgerE2904}.

		Second, when processes do not meet the second condition, i.e. processes which do not achieve high NTIC will remain unconscious. This can explain why many "policy-based" processes are not conscious.\todo{Need a better term/way here} Policy-based here features those processes taking sensory information as input and directly outputting actions. Therefore, the future states of policy-based processes largely depend on the environmental states and failed to achieve informational closure. Neural processes are included in this category, e.g. reflexive neural circuit, blindsight, procedure memory.

		To summarise, our theory can well explain the various findings with parsimonious assumptions.

	    \begin{ants}
	        @ \rewrite{the nonsemantic processing of primes is enhanced and priming effects are boosted when the experimental context allows the formation of automatic stimulus–response mappings.}\cite{VandenBussche2009}
	    \end{ants}

@@

	\section{Comparison with other theories}
		\ideaBox{Main points should be same/diff, our advantages, and predictions}
		In this section, we will discuss the relationship between our theory and other popular modern theories of consciousness.

\rlstart{2}
		\subsection{Theories about multilevel views on consciousness and cognition}
        Previously, multilevel views on consciousness and cognition have been proposed. We shortly describe two theories which is \todo{XXX and XXX} related to our current proposal.	% We discussed the differences between our theory and other theories about multilevel views.

            \subsubsection{level of Organisation \cite{wimsatt1994ontology}}
                As mentioned previously, the level of coarse-graining is different from the anatomical level.
                Pennartz focus more on multimodal representation as the most important factor (See the discussion in \cite{pennartz2015brain}). Our proposal is inline with Pennartz's Neurorepresentational  theory (Neurorepresentationalism) \cite{pennartz2018consciousness,pennartz2015brain}. However, it’s crucial to note that our theory claims only the level of coarse-graining achieving NTIC matters to consciousness rather than the anatomical level of sensory hierarchy. 
                \ideaBox{Should I also deal with Marr's level of abstraction?}

			\subsubsection{Intermediate Level Theory} \label{IntermediateLevelTheory}
                One important theory linking consciousness to multilevel views is the Intermediate Level Theory (ILT). ILT proposes that conscious experience only correlates specific levels of representations in the sensory processing the hierarchy. This theory claims that consciousness only associates with the representation at intermediate levels rather than the ones at lower-level or higher-level discribed as 2.5D. However, ILT focuses on the levels in terms of anatomical direction. As mentioned previously, a critical difference between ILT and our theory is that our theory doesn't assume the direction of coarse-graining should align with the direction of anatomical processing levels along cortical hierarchies (see fig \ref{fig:hierarchy}).

                Different from ILT which suggests that the neural substrates responsible for the 2.5D computation is conscious, we predict that if information that is carried by v1 neurons are necessary to complete informational closure, the states of V1 neurons should also co-vary with conscious contents.

			\subsubsection{Pennartz's neurorepresentational theory (Neurorepresentationalism)}
			    Our theory shares some similar concepts with Pennartz's Neurorepresentationalism. However, Neurorepresentationalism focuses on multimodal representation \cite{pennartz2018consciousness,pennartz2015brain}. Another focus of neurorepresentationalism is on "making sense" between representations\todo{Need something here}. Different from neurorepresentationalism, conscious contents in our framework are grounded by the informational relations between variables in NTIC because NTIC provides a closed relationship between states in a system.

			    Similar to Neurorepresentationalism, our framwork is more close to Marr ’ s original distinction between the levels of (neural) implementation, algorithms, and computational theory [122], but focuses on how conscious representations correspond to computational operations at levels with lower complexity and representational capacity.\cite{pennartz2018consciousness,pennartz2015brain}

			    Neurorepresentationalism is also a functionalist perspective. However, e don't assume any functional properties as the criteria of consciousness. Instead, we propose information as a more fundamental principle correlates consciousness.

		        \begin{WritingMaterials}
				%% Back up materials

@@

@@

				%% Our theory
				@ However, as we mentioned in Section \ref{sec:SensoryHierarchy}, \rewrite{The notion of ‘ levels ’ deployed here is functional and very different from that of successive anatomical processing stages along cortical hierarchies [75] or from anatomic scales in the brain. The multi-level concept in [2] is more akin to Marr ’ s original distinction between the levels of (neural) implementation, algorithms, and computational theory [122], but focuses on how conscious representations correspond to computational operations at levels with lower complexity and representational capacity.}\cite{pennartz2018consciousness,pennartz2015brain}
			\end{WritingMaterials}

@@

\rlstart{2}	
		\subsection{First-order theories}
            The first-order theories suggest that consciousness is determined by early sensory information or neural activities\needref{First-order theories}. The first-orde view maintains that conscious awareness is determined by early sensory activity alone, independently of higher-order representations. \rewrite{According to first-order views, phenomenal consciousness consists in analog or fine-grained contents that are available to the first-order processes that guide thought and action. So a phenomenally-conscious percept of red, for example, consists in a state with the analog content red which is tokened in such a way as to feed into thoughts about red, or into actions that are in one way or another guided by redness.}

            We predict that, if early sensory information or neural activities after coarse-graining take parts in the NTIC process, early sensory information or neural activities also contribute consciousness. However, due to coarse-graining, changes of early sensory information or neural activities do not necessarily accompany with changes of conscious contents. \todo{Need more here, espectially more counterintuitive predictions}

			\begin{WritingMaterials}
				@ \rewrite{
					The ﬁrst-order view maintains that conscious awareness is determined by early sensory activity alone, independently of higher-order representations. Thus the crucial difference between the ﬁrst-order and higher-order views is that the latter but not the former predict that conscious awareness is determined at least in part by prefrontal and parietal activity. Therefore, in the group of ﬁrst-order theorists we include here not only those commonly labeled as such in the philosophical literature [11] but also theorists, such as Ned Block [12,13], who hold that the phenomenal qualities of awareness depend on the biological substrate rather than merely the content of the ﬁrst-order representations, as well as scientists who hold that visual awareness depends on activity in content-speciﬁc regions of the extrastriate cortex [24,25] or on feedback from these regions to the primary visual cortex [26]. Most ﬁrst-order theories explain the difference between awareness and unawareness by positing that the latter is associated with weak information [29] or with representations in alternative (e.g. subcortical) sensory pathways. Thus this view suggests that conscious and unconscious processing will have different functional consequences. Whereas some ﬁrst-order theorists hold that some higher cognitive functions can be performed without conscious awareness [30–32], most ﬁrst-order theorists take a difference in perceptual task performance (e.g. ‘hits’ vs ‘misses’ in a detection task) as evidence for a difference in conscious awareness [12,13,25,26,33]. In other words, they typically associate task performance with awareness..} \cite{lau2011empirical}

@@

\rlstart{1}
		\subsection{Higher Order Thought theory of consciousness}
		    In contrast to first-order theories, higher-order thought theories suggest that consciousness depends on higher-order representations representing agents as being in particular internal states. Meta-cognition is also associated with many conscious cognitive function. However, we propose a new perspective and indicate that HOT may be a misunderstanding \critical{Very bad writing. I need to rewrite this part}. This may be the result of neural coarse-graining. Because contents in informational closure look like watching fine-grained information, people may have an wrong impression about it. Coarse-grained information can be summary statistics which may be misunderstood as higher-order representation. It is true that the neural system does create  meta-representation to represent xxx\needref{Maybe come studies about confidence represenatation}. The higher-order representation may resemble coarse-grained variables. This may cause misidentify the entity which correlates conscious experience.

		    Moreover, the predictive information in NTIC is critical for other systems to build forward models for a wild range of tasks. Therefore, most of the high level cognition can utilise the state of informational closure. For example, mental planning needs a precise forward model to infer the environmental dynamics.

			\begin{WritingMaterials}
		    @ In contrast to first-order theories, higher-order thought theories suggest that consciousness depends on higher-order representations representing agents as being in particular internal states.

@@

			@ \cite{rosenthal2005consciousness}

            @ ============================================================================
			@ \rewrite{
				Higher-order theories of consciousness argue that conscious awareness crucially depends on higher-order mental representations that represent oneself as being in particular mental states.} \cite{lau2011empirical}

@@

\rlstart{2}
		\subsection{Global workspace theory}
		Global workspace theory (GWT)\cite{baars1988cognitive, baars1997theatre, baars2002conscious} or Global Neuronal Workspace theory (GNWT)\cite{dehaene1998neuronal, dehaene2001towards, dehaene2011experimental} states that the neural system consists of many separate specialised modules and a central global workspace (GW) which integrates and passes information amount the modules. Only the information that is accessed by the global workspace can be conscious aware of. The modules competes with each other to gain the access to the global workspace and the information from the winner can trigger an all-or-none "ignition" in the global workspace and be globally broadcasted to other modules. Conscious contents then associates information which gains access to the internal global workspace \cite{Dehaene2017}. Our framework can well accommodate and interpret these claims by GWT.

		Stability: Conscious perception necessitates representational stability. Our theory rests upon self-predictability which formally encompasses stability.

		Broadcasting: When new sensory information from a modality is involved in NTIC, the information can be preserved in the following dynamic of NTIC. The neural system can extract the information for specific task goals. This is equivalent to the function of broadcasting.

		Non-linear ignition: Because mapping microscopic to macroscopic states is many-to-one, it commonly shows a nonlinear relationship between microstates and macrostates. In our theory, new information presents in conscious perception corresponds to a transition in the state space of the NTIC process. This can cause a significant change of the brain states and resembles non-linear ignition of brain activities. Conscious access as an accumulation of evidence leading to an all-or-none ignition What, if anything, remains unique to conscious processing? Although many cognitive operations can be partially launched non-consciously, these operations rarely if ever run to completion in the absence of consciousness. A subliminal stimulus may induce above-chance performance, behavioural priming, and a small amount of brain activity in narrowly deﬁned brain networks, but these measures often increase dramatically as soon as the subject reports seeing the stimulus, especially in high-level areas [46 60,61  ]. Accumulation of evidence has been demonstrated with non-conscious stimuli [59], but only conscious stimuli cross the threshold beyond which an overt strategy can be ﬂexibly deployed. \todo{Cite similar opinion from other theories}

		A difference between our theory and GWT is that our theory does not suggest a neuronal core anatomical area for consciousness. \todo{Link to Section 4}. Coarse-grained information in NTIC is more crucial for consciousness rather than neural substrates supporting the global workspace.
